Think deep for reef resilience

### 2025-09-18 paper/paper_draft.qmd
Update Julia-rendered table to ensure proper rendering and label/caption attachment in word output

The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of
thousands of individual reefs. They are interconnected through coral and fish larval
dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@cappo2000].
The GBR faces severe projected coral cover declines under climate change [@bozec2025;
@bozec2022; @condie2021]. These coral cover declines will be compounded by ocean
acidification, tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012;
@fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. The 2023-24 Summer mass
bleaching event may be signalling a shift towards this reef future, with some level of
bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs)
[@australianinstituteofmarinescience2024]; @cantin2024\].

@@

```{julia}
#| echo: false
#| warning: false
#| message: false
#| results: asis
#| label: stbl-cluster-cid
#| tbl-cap: Complexity invariant distance (CID) between low and high cluster median time series in each management area under each GCM. CID values are calculated for percentage cover time series (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) time series (@sfig-gcm-dhw-trajectories). Complexity invariant distance represents the Euclidean distance between time series, corrected by the complexity of the two time series. CID values are used to quantify overall differences between these two cluster levels at management area and GCM levels. CID values for percentage cover and DHW time series are not directly comparable as the time series use different units.

using PrettyTables, Markdown
cd("../src")
include("../src/ADRIA/HighResCoralStress/6_quantifying_cluster_differences.jl"); # Quantify low-high cluster differences using CID metric.

io = IOBuffer()

header = ["GCM", "Management area", "CID - cover", "CID - DHW"]
pretty_table(io, distances, backend=Val(:markdown), header=header)

md_string = (String(take!(io)))
Markdown.parse(md_string)
```

>>>>

The Great Barrier Reef (GBR) is the world's largest coral reef ecosystem consisting of
thousands of individual reefs. They are interconnected through coral and fish larval
dispersal patterns mediated by hydrodynamic, spatial, and ecological processes [@cappo2000].
The GBR faces severe projected coral cover declines under climate change [@bozec2025;
@bozec2022; @condie2021]. These coral cover declines will be compounded by ocean
acidification, tropical cyclones, and crown-of-thorns starfish outbreaks [@death2012;
@fox-kemper2021; @seneviratne2021; @sweatman2011; @wolff2018]. The 2023-24 Summer mass
bleaching event may be signalling a shift towards this reef future, with some level of
bleaching recorded on 79% of surveyed reefs (total 1001 surveyed reefs)
[@australianinstituteofmarinescience2024; @cantin2024].

@@

```{julia}
#| echo: false
#| warning: false
#| message: false
#| output: asis

cap = """
Complexity invariant distance (CID) between low and high cluster median time series in each management area under each GCM. CID values are calculated for percentage cover time series (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) time series (@sfig-gcm-dhw-trajectories). Complexity invariant distance represents the Euclidean distance between time series, corrected by the complexity of the two time series. CID values are used to quantify overall differences between these two cluster levels at management area and GCM levels. CID values for percentage cover and DHW time series are not directly comparable as the time series use different units.
"""
using Markdown,Tables,MarkdownTables
cd("../src")
include("../src/ADRIA/HighResCoralStress/6_quantifying_cluster_differences.jl"); # Quantify low-high cluster differences using CID metric.
rename!(distances, 
    "management_area" => "Management area",
    "CID_cover" => "CID - cover",
    "CID_dhw" => "CID - DHW"
)
print("""
::: {.table #stbl-cluster-cid}
$(markdown_table(distances, String))

$(cap)
:::
""")
```
